% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot[L]{Aleksandr Michuda, +1-718-564-9741}
\fancyfoot[R]{\thepage}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
%A Few Useful Packages
% \usepackage{marvosym}
% \usepackage{fontspec} 					%for loading fonts
% \usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
% \usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
% \usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\def\toprule{}
\def\bottomrule{}
\def\midrule{}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{3pt}{10pt}{10pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{aleksandr-michuda}{%
\section{Aleksandr Michuda}\label{aleksandr-michuda}}

\textbf{Email}:
\href{mailto:am2497@cornell.edu}{\nolinkurl{am2497@cornell.edu}}

\textbf{Website}: \href{https://amichuda.github.io}{amichuda.github.io}

\textbf{Github}: \href{https://github.com/amichuda}{github.com/amichuda}

\textbf{Linkedin}:
\href{https://www.linkedin.com/in/aleksandr-michuda}{www.linkedin.com/in/aleksandr-michuda}

\hypertarget{appointments}{%
\section{Appointments}\label{appointments}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0556}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2778}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.6667}}@{}}
\toprule
\endhead
2021+ & Assistant Research Professor & Center for Data Science for
Enterprise and Society, Cornell University \\
\bottomrule
\end{longtable}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{longtable}[]{@{}lll@{}}
\toprule
\endhead
2021 & Agricultural and Resource Economics, UC Davis & PhD \\
2014 & Economics CUNY Hunter College & BA/MA \\
2014 & Philosophy CUNY Hunter College & BA \\
\bottomrule
\end{longtable}

\hypertarget{publications-and-working-papers}{%
\section{Publications and Working
Papers}\label{publications-and-working-papers}}

\hypertarget{development-economics}{%
\subsection{Development Economics}\label{development-economics}}

\href{https://academic.oup.com/cdn/article/5/Supplement_2/693/6292849}{Vosti,
Stephen, Katherine Adams, Aleksandr Michuda, Hanqi Luo, Demewoz
Woldegebreal, Victoria Chou, Adrienne Clermont, Ismael Teta, Alex
Ndjebayi, Jules Guintang, Reina Engle-Stone. ``Selecting Micronutrient
Intervention Programs to Save Lives: Evidence From Cameroon''}
\emph{Annals of the New York Academy of Sciences forthcoming}

\href{https://onlinelibrary.wiley.com/doi/full/10.1111/ajae.12178}{Gupta,
Anubhab, Heng Zhu, Miki Khanh Doan, Aleksandr Michuda, and Binoy
Majumder. ``Economic Impacts of the COVID-19 Lockdown in a
Remittance‐dependent Region.'' \emph{American Journal of Agricultural
Economics.}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Working Papers}

\href{https://drive.google.com/file/d/1sqC0W1mUMzPzQreimT22qnqsnNlIj3bc/view?usp=sharing}{Michuda,
Aleksandr, Cristina Chiarella, Oscar Barriga-Cabanillas, and Juan
Sebastian Correa. ``Genetic Dilution erodes productivity: Exploring
farmers' low adoption levels of improved maize in Ethiopia.'' (2022)}

\href{https://drive.google.com/file/d/14VANz8V45C6bIX1d4__IMmOn5xNJM5a7/view?usp=sharing}{Michuda,
Aleksandr. ``Rural-Urban Risk Sharing Networks: Uber Driver Labor Supply
Responses To Shocks In Uganda.'' (2022)} \emph{Submitted}

\href{https://scholar.google.com/scholar_url?url=https://ageconsearch.umn.edu/record/322365/files/24195.pdf\&hl=en\&sa=T\&oi=gsb-gga\&ct=res\&cd=2\&d=12962046704729585600\&ei=7e1vY4C5MIqUy9YP-OmKyAQ\&scisig=AAGBfm2aaJtfS_KnDh5hRc47a4cZxX41aw}{Doan,
Miki Khanh, Aleksandr Michuda, Heng Zhu, Anubhab Gupta, and Binoy
Majumder. ``Livelihood Strategies in a Climate-change Vulnerable
Region.'' (2022)}

\hypertarget{political-economy}{%
\section{Political Economy}\label{political-economy}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Working Papers}

\href{https://drive.google.com/file/d/1ZCS0c89GkS4hio5WEUrMSnqJ1FYeMd0V/view?usp=sharing}{Michuda,
Aleksandr, and Michael Kevane. ``Classification into ethnic groups in
Burkina Faso using names and localities.'' (2022)}

\href{https://drive.google.com/file/d/1Tdmr2_4DCSXIt_Q7tq1omglsgn249VgE/view?usp=sharing}{Bird,
Samuel S.; Michuda, Aleksandr. ``Measuring Ethnicity and Estimating its
Effects on Voting at Scale: Evidence from Uganda.'' (2022)}

\hypertarget{applied-econometrics-and-software}{%
\subsection{Applied Econometrics and
Software}\label{applied-econometrics-and-software}}

\href{https://academic.oup.com/cdn/article/6/Supplement_1/776/6606969}{Michuda,
A., Ortiz-Becerra, K., Adams, K., Jarvis, M., Somda, H., Arnold, C.,
\ldots{} \& Vosti, S. (2022). minimod: An Open Source Python Package to
Evaluate the Cost Effectiveness of Micronutrient Intervention Programs.
\emph{Current Developments in Nutrition, 6(Supplement\_1)}, 776-776.}

\href{https://journals.sagepub.com/doi/abs/10.1177/1536867X1801800109}{Cabanillas,
Oscar Barriga, Jeffrey D. Michler, Aleksandr Michuda, and Emilia
Tjernström. ``Fitting and interpreting correlated random-coefficient
models using Stata.'' \emph{Stata Journal} 18, no. 1 (2018): 159-173.}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Working Papers}

\href{https://emiliatjernstrom.com/files/TGBLMM2020.pdf}{Tjernström,
Emilia, Dalia Ghanem, Oscar Barriga Cabanillas, Travis J. Lybbert,
Jeffrey D. Michler, and Aleksandr Michuda. ``A Group Random Coefficient
Approach to Modeling Heterogeneous Returns to Technology Adoption.''
(2021)}

\hypertarget{agricultural-economics}{%
\subsection{Agricultural Economics}\label{agricultural-economics}}

\href{https://www.mdpi.com/2073-4395/11/1/149}{Michuda, Aleksandr,
Rachael E. Goodhue, Mark Hoffmann, and Steven A. Fennimore. ``Predicting
Net Returns of Organic and Conventional Strawberry Following Soil
Disinfestation with Steam or Steam Plus Additives.'' \emph{Agronomy} 11,
no. 1 (2021): 149.}

\href{https://www.tandfonline.com/doi/full/10.1080/21683565.2018.1552228?casa_token=uUSSMSYYz8kAAAAA\%3Ak9RAJxZUEeAcikUZH9G-o5hGAd21QvhnQVWkPpecl--ZYyfr0R10XscXW60Ohs4KF7S5S2Pa_HFp}{Michuda,
Aleksandr, Rachael Goodhue, Karen Klonsky, Graeme Baird, Lucinda Toyama,
Margherita Zavatta, Joji Muramoto, and Carol Shennan. ``The economic
viability of suppressive crop rotations for the control of verticillium
wilt in organic strawberry production.'' \emph{Agroecology and
Sustainable Food Systems} 43, no. 9 (2019): 984-1008.}

\href{https://giannini.ucop.edu/publications/are-update/issues/2017/20/6/crop-rotations-can-increase-net-returns-in-organic/}{Michuda,
Aleksandr, Rachael Goodhue, Joji Muramoto, and Carol Shennan. ``Crop
Rotations Can Increase Net Returns in Organic Strawberry and Vegetable
Production Systems.'' \emph{ARE Update} 20(6)(2017): 5-8. University of
California Giannini Foundation of Agricultural Economics.}

\hypertarget{book-chapters}{%
\section{Book Chapters}\label{book-chapters}}

\href{https://link.springer.com/chapter/10.1007/978-3-030-14000-7_11}{Carter,
Michael R., and Aleksandr Michuda. ``The Distribution of Productive
Assets and the Economics of Rural Development and Poverty Reduction.''
In The Palgrave Handbook of Development Economics, pp.~377-408. Palgrave
Macmillan, Cham, 2019.}

\hypertarget{languages-and-skills}{%
\section{Languages and Skills}\label{languages-and-skills}}

English: Fluent

Russian: Fluent

Ukrainian: Basic Knowledge

\hypertarget{technical-skills}{%
\section{Technical Skills}\label{technical-skills}}

Python, GAMS, Stata, LaTeX, R, GitHub, Bash

\hypertarget{past-experience}{%
\section{Past Experience}\label{past-experience}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1923}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.6250}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1827}}@{}}
\toprule
\endhead
Consultant & MINIMOD - Optimal Nutritional Interventions across Space
and Time & January 2020 - July 2022 \\
Data Science Intern & Uber & September 2019 - December 2019 \\
Catalyst & BITSS (Berkeley Initiative for Transparency in the Social
Sciences) & July 2017 - Present \\
Research Assistant & UC Davis - Disease Suppressive Crop Rotations &
July 2016 - September 2019 \\
\bottomrule
\end{longtable}

\hypertarget{peer-review}{%
\section{Peer Review}\label{peer-review}}

\begin{itemize}
\tightlist
\item
  \href{https://agrifoodecon.springeropen.com/}{Journal of Agricultural
  and Food Economics}
\item
  \href{https://onlinelibrary.wiley.com/journal/14678276}{American
  Journal of Agricultural Economics}
\end{itemize}

\hypertarget{conferences}{%
\section{Conferences}\label{conferences}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2353}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7647}}@{}}
\toprule
\endhead
NEUDC 2022 & Genetic Dilution erodes productivity: Exploring farmers'
low adoption levels of improved maize in Ethiopia \\
Pacdev 2022 & Urban Labor Supply Responses to Rural Drought Shocks on
Rideshare Platforms. \\
NEUDC 2021 & Urban Labor Supply Responses to Rural Drought Shocks on
Rideshare Platforms. \\
BITSS RT2 2020 & Dynamic Documents with Jupyter Notebooks \\
AAEA Meetings 2019 & Evaluating a Systems Approach to Suppressive Crop
Rotations in Strawberry Production \\
AAEA Meetings 2018 & Political Contributions and the Case of South
African Land Reform \\
AAEA Meetings 2017 & The Economic Viability of Suppressive Crop
Rotations in Organic Strawberry Production \\
& Empirically Estimating the Impact of Weather on Agriculture \\
EEA Conference 2014 & The Russian Mir and Agrarian Transition \\
CUNY's UGRC 2013 & Large Frontiers and Coercion: An Economic
Perspective \\
\bottomrule
\end{longtable}

\hypertarget{scholarships-and-awards}{%
\section{Scholarships and Awards}\label{scholarships-and-awards}}

\small

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2771}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7229}}@{}}
\toprule
\endhead
Summer 2022 & NSF OSP: 142678 \\
& Conference on Reproducibility and Replicability in Economics and
Social Sciences (CRRESS) \\
Summer 2022 & Dyson AEP Faculty Seed Grant \\
& The Surname-Ethnicity Connection: A Validation Exercise \\
Spring 2022 & Dyson AEP Faculty Seed Grant \\
& Climate induced soil salinity impacts on agricultural productivity and
livelihood diversification in the Sundarbans, India \\
Winter 2021 & (CGIAR) SPIA small grant for agricultural innovations in
Ethiopia \\
Fall 2014 - Spring 2016 & Steindler Fellowship \\
Spring 2017 & Henry A. Jastro Grant \\
Fall 2017 & BITSS Catalyst Grant \\
2017 & Graduate Student Association President \\
\bottomrule
\end{longtable}

\end{document}
